Trends of SDR in Thessaloniki

### 2023-10-13 Article.Rmd
Commit 2023-10-13 13:28

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Athanasios Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CHP1 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    Mainreferences.bib
linenumbers:     false
numbersections:  true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
output: 
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
  bookdown::word_document2: default
  rticles::elsevier_article:
    keep_tex:         no
    citation_package: natbib
# date:           "`r format(Sys.time(), '%F')`"
---

@@

```{r cusum, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCuSum-1.png",    # ALL sky
    "./images/CumulativeDailyCuSum-5.png",    # CLEAR sky
    "./images/CumulativeDailyCuSum-9.png"))   # Cloud sky
```

@@

```{r cusumnotrend, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR after removing the long term trend from the daily values.', fig.subcap=c('All-skies.', 'Clear-skies.', 'Cloud-skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3}
knitr::include_graphics(c(
    "./images/CumulativeDailyCuSumNOtrend-1.png",    # ALL sky
    "./images/CumulativeDailyCuSumNOtrend-5.png",    # CLEAR sky
    "./images/CumulativeDailyCuSumNOtrend-9.png"))   # Cloud sky
```

>>>>

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Athanasios Natsis 
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CHP1 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:         "An awesome journal"
date:            "`r Sys.Date()`"
classoption:     preprint, 3p, authoryear
bibliography:    Mainreferences.bib
linenumbers:     false
numbersections:  true
header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
output: 
  rticles::elsevier_article:
    keep_tex:         no
    citation_package: natbib
  bookdown::word_document2: default
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              no
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
# date:           "`r format(Sys.time(), '%F')`"
---

@@

<!-- ```{r cusum, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR.', fig.subcap=c('All-sky conditions.', 'Clear-sky conditions.', 'Cloud-sky conditions.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics(c( -->
<!--     "./images/CumulativeDailyCuSum-1.png",    # ALL sky -->
<!--     "./images/CumulativeDailyCuSum-5.png",    # CLEAR sky -->
<!--     "./images/CumulativeDailyCuSum-9.png"))   # Cloud sky -->
<!-- ``` -->

@@

<!-- ```{r cusumnotrend, echo = FALSE, fig.cap='Running cumulative sum plots of the daily SDR after removing the long term trend from the daily values.', fig.subcap=c('All-skies.', 'Clear-skies.', 'Cloud-skies.'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics(c( -->
<!--     "./images/CumulativeDailyCuSumNOtrend-1.png",    # ALL sky -->
<!--     "./images/CumulativeDailyCuSumNOtrend-5.png",    # CLEAR sky -->
<!--     "./images/CumulativeDailyCuSumNOtrend-9.png"))   # Cloud sky -->
<!-- ``` -->
